Implementing Adaptive Preregistration with Git and Github

### 2023-10-16 adaptive_preregistration_implementation.qmd
update old images and reflect current github workflow

-   View the document in GitHub [here](https://github.com/egouldo/VEFMAP_VEG_Stage6/blob/master/analysis/preregistration_template.Rmd)
-   Click on The 'edit document' button: ![Screen Shot 2020-05-10 at 6 29 33 pm](https://user-images.githubusercontent.com/8400682/81494459-791b7080-92ec-11ea-979b-900317b4a9b6.png)
-   You will be able to edit the document directly in GitHub, Edit away!

@@

![Screen Shot 2020-05-18 at 12 19 29 pm](https://user-images.githubusercontent.com/8400682/82168463-2b14f700-9902-11ea-95a0-21fe385629bb.png)

>>>>

-   View the document in GitHub [here](https://github.com/egouldo/VEFMAP_VEG_Stage6/blob/master/analysis/preregistration_template.Rmd)
-   Click on The 'edit document' button: ![](https://github.com/egouldo/VEFMAP_VEG_Stage6/assets/8400682/dd6ee5b6-9595-46e0-8576-7d2a3c7e2c9a)
-   You will be able to edit the document directly in GitHub, Edit away!

@@

![](https://github.com/egouldo/VEFMAP_VEG_Stage6/assets/8400682/55fe090c-b72c-45f4-808f-039960796dc0.png)
